### 2015-07-14 chapters/ipa_meets_unicode.tex
typo
reordered last pitfall; added subsections to IPA

\subsubsection*{Brief history}

@@

\subsubsection*{Principles}

@@

\subsubsection*{Computational representation}

@@

\subsubsection*{SAMPA and X-SAMPA}

@@

\subsubsection*{The need for a single multilingual environment}

@@

\subsubsection*{Unicode and ISO 10646}

@@

\subsubsection*{IPA and Unicode}

@@

In the major revision of the IPA in 1932, affricates were represented by two consonants 
(e.g.\ <tʃ>), or ligatures <ʧ>, or with the tie-bar <t͡s>. In the 1938 revision the tie-bar's 
semantics were broadened to indicate simultaneous articulation, e.g.\ in labial velars 
such as <k͡p>. Thus the tie-bar is a convenient diacritic for visually tokenizing input 
strings into chunks of phonetically salient groups, including affricates, doubly articulated 
consonants or diphthongs.

>>>>

\subsection{Brief history}

@@

\subsection{Principles}

@@

\subsection{Computational representation}

@@

\subsection{SAMPA and X-SAMPA}

@@

\subsection{The need for a single multilingual environment}

@@

\subsection{Unicode and ISO 10646}

@@

\subsection{IPA and Unicode}

@@

In the major revision of the IPA in 1932, affricates were represented by two consonants 
(e.g.\ <tʃ>), or ligatures <ʧ>, or with the tie-bar <t͡ʃ>. In the 1938 revision the tie-bar's 
semantics were broadened to indicate simultaneous articulation, e.g.\ in labial velars 
such as <k͡p>. Thus the tie-bar is a convenient diacritic for visually tokenizing input 
strings into chunks of phonetically salient groups, including affricates, doubly articulated 
consonants or diphthongs.
